An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2020-07-09 gas-adsorption/rsc-gas-ads-complete.tex
more edits, including abstract rewrite

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{An upper bound to gas storage and delivery via pressure-swing adsorption in
porous materials$^\dag$}} \\%Article title goes here instead of the text "This is the title"
\vspace{0.3cm} & \vspace{0.3cm} \\

 & \noindent\large{Jordan K. Pommerenck,$^{\ast}$\textit{$^{a}$} Cory M. Simon,\textit{$^{b\ddag}$} and David Roundy\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.

\includegraphics{head_foot/dates} & \noindent\normalsize{The abstract should be a single paragraph which summarises the content of the article. Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."

@@

%%%FOOTNOTES%%%

\footnotetext{\textit{$^{a}$~Address, Address, Town, Country. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: xxxx@aaa.bbb.ccc}}
\footnotetext{\textit{$^{b}$~Address, Address, Town, Country. }}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 00.0000/00000000.}
%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

@@

\section*{Conflicts of interest}
In accordance with our policy on \href{http://www.rsc.org/journals-books-databases/journal-authors-reviewers/author-responsibilities/#code-of-conduct}{Conflicts of interest} please ensure that a conflicts of interest statement is included in your manuscript here.  Please note that this statement is required for all submitted manuscripts.  If no conflicts exist, please state that ``There are no conflicts to declare''.

\section*{Acknowledgements}
The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.

>>>>

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{An upper bound to gas storage and delivery via pressure-swing adsorption in
porous materials}} \\%Article title goes here instead of the text "This is the title"
\vspace{0.3cm} & \vspace{0.3cm} \\

 & \noindent\large{Jordan K. Pommerenck,$^{\ast}$\textit{$^{a}$} Cory M. Simon,\textit{$^{b}$} and David Roundy\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.

\includegraphics{head_foot/dates} & \noindent\normalsize{
    Both hydrogen
and natural gas are challenging to economically store onboard vehicles as
fuels, due to their low volumetric energy density at ambient conditions.
One strategy to densify
these gases is to pack the fuel tank with a porous
adsorbent material.
% 
The US Department of
Energy (DOE) has set volumetric deliverable capacity
targets which, if met, would help
enable commercial adoption of hydrogen/natural gas as transportation fuels.
%
%Many have attempted to establish theoretical upper bounds on the deliverable
%capacity via pressure-swing adsorption using simplified models of the
%gas-substrate and gas-gas interaction~\cite{gomez2014exploring,
%gomez2017impact, kaija2018high, lee2019predicting}; none have established a
%rigorous upper bound on the deliverable capacity.
%
Here, we present a
theoretical upper bound on the deliverable capacity of a gas in a rigid
porous
material via an isothermal pressure swing.
%
To provide an extremum, we consider
a substrate that provides a spatially uniform potential energy field for the
gas. Our bound is unique in that it relies directly on experimentally measured
properties of the pure gas.
%
We conclude
that the goals set by the DOE for room-temperature natural gas and hydrogen
storage are just barely theoretically possible.
The goals are likely to be impossible for any real,
rigid porous material because of steric
repulsion, which must reduce the capacity below our upper
bound. Limitations
to the scope of applicability of our upper bound may guide fuel tank design and
future material development. Firstly, one could avoid using an \emph{isothermal}
pressure swing by heating the adsorbent to drive off
trapped, residual gas. Secondly,
our upper bound assumes the material does not change its
structure in response to adsorbed gas, suggesting that flexible materials could
still satisfy the DOE targets.}

%Any references in the abstract should be written out in full \textit{e.g.}\ [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].} \\%The abstrast goes here instead of the text "The abstract should be..."

@@

%%%FOOTNOTES%%%
\footnotetext{\textit{$^{*}$~E-mail: pommerjo@oregonstate.edu}}
\footnotetext{\textit{$^{a}$~Department of Physics, Oregon State University, Corvallis, OR 97331, USA.}}
\footnotetext{\textit{$^{b}$~Department of Chemical, Biological, and Environmental Engineering, Oregon State University, Corvallis, OR 97331, USA. }}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.

%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 00.0000/00000000.}

%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \textit{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

@@

\section*{Conflicts of interest}
There are no conflicts to declare.

%\section*{Acknowledgements}
%The Acknowledgements come at the end of an article after Conflicts of interest and before the Notes and references.
